3D Magnetic modelling of ellipsoidal bodies

### 2017-02-17 manuscript/manuscript.tex
write the fields in the main coordinate system

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any uniformly magnetized body in a given direction.
By presuming that this uniform magnetization is due to
induction and that it is proportional to the resulting
magnetic field (intensity) inside the body, he postulated 
that the resulting field must also be uniform and 
parallel to the magnetization. This uniformity is due to
the fact that the resulting field is defined as the
negative gradient of the magnetic scalar potential.
As a consequence of this uniformity, 
the gravitational potential $U$ at points within the 
body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform magnetic field.
This property can be extended to other bodies
defined as limiting cases of an ellipsoid
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field.

@@

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre
(Fig. \ref{fig:orientation-angles}b).
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
(Eq. \ref{eq:A}) is defined according to the ellipsoid type.

@@

Consider a magnetized ellipsoid immersed in
a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
given by
\begin{equation}
\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
\begin{array}{c}
\cos I \: \cos D \\
\cos I \: \sin D \\
\sin I
\end{array}
\right] \: ,
\label{eq:H0}
\end{equation}
where $\| \cdot \|$ denotes the Euclidean norm and
$D$ and $I$ are respectively, the declination and inclination of the 
local-geomagnetic field in the main coordinate system
(Fig. \ref{fig:orientation-angles}a).
This uniform field can be, for example, the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:V-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Eq. \ref{eq:V-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896, reitz1992, sttraton2007}.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system (Fig. \ref{fig:orientation-angles}a)
into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system (Fig. \ref{fig:orientation-angles}b).
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
peake1953, chang1961, macmillan1958, lowes1974,  clark1986, 
tejedor1995, sttraton2007}.

@@

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in 
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the uniform magnetic field $\tilde{\mathbf{H}}_{0}$ 
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq.\ref{eq:M-remanence} by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference $\theta$ between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

@@

The magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
produced by an ellipsoid at external points is calculated from 
Eqs. \ref{eq:H-tilde} and \ref{eq:M-tilde-remanence} as the difference
between the resultant field $\tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
and the uniform field $\tilde{\mathbf{H}}_{0}$:
\begin{equation}
\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}}) = 
- \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
\label{eq:delta-H-tilde}
\end{equation}
The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
Eq. \ref{eq:delta-H-tilde} will be presented in
the following section.

The $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
can be interpreted as a uniformly magnetized body located in the
crust while the uniform field $\tilde{\mathbf{H}}_{0}$ can
be interpreted as the main component of the geomagnetic field
on the study area, which is commonly assumed to be
generated at the liquid part of the Earth's core.
Equation \ref{eq:delta-H-tilde} gives the magnetic field
(in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
in geophysics, the most widely used field is the magnetic 
induction (in \unit{nT}). Fortunately, this conversion can
be easily done by multiplying Eq. \ref{eq:delta-H-tilde}
by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
magnetic constant (in \unit{H \, m^{-1}}).
For geophysical applications, it is preferable to
calculate the total-field anomaly produced by the
magnetic sources. This scalar quantity is given by
\citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) = \| 
\mathbf{B}_{0} + \Delta \mathbf{B}(\mathbf{r}) \|
- \| \mathbf{B}_{0} \| \: ,
\label{eq:delta-T}
\end{equation}
where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
(Eq. \ref{eq:H0}) and $\Delta \mathbf{B}(\mathbf{r}) = 
k_{m} \, \mathbf{V} \; \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$,
with $\mathbf{V}$ defined according to the ellipsoid type and
$\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ defined by
Eq. \ref{eq:delta-H-tilde}.
In practical situations, however, 
$\| \mathbf{B}_{0} \| >> \| \Delta \mathbf{B}(\mathbf{r}) \|$
and, consequently, the following approximation is valid \citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) \approx  
\frac{\mathbf{B}_{0}^{\top} \Delta \mathbf{B}(\mathbf{r})}{\| \mathbf{B}_{0} \|} \: .
\label{eq:delta-T-approx}
\end{equation}

@@

The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\dagger}$ used to compute the 
uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) and the magnetization $\tilde{\mathbf{M}}$ 
(Eqs. \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence})
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by 
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the  
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the 
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
do not depend on the transformed position
vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the SI
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
Notice that, according to Eqs. \ref{eq:H-tilde} 
and \ref{eq:N-tilde-VT-N-V},
\begin{equation}
\mathbf{N}(\mathbf{r}) = 
\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
\mathbf{V}^{\top} \: ,
\label{eq:N-V-N-dagger-VT}
\end{equation}
where $\tilde{\mathbf{N}}^{\dagger}$ (Eqs. \ref{eq:Hi-tilde}, 
\ref{eq:M-tilde} and \ref{eq:M-tilde-remanence}) is a diagonal 
matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
This equation shows that, for the particular case 
in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
represent a point inside the
volume $\vartheta$ of the ellipsoid, the elements 
$\tilde{n}^{\dagger}_{ii}$ (Eq. \ref{eq:n-tilde-dagger-ii})
of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
columns of $\mathbf{V}$ represent the eigenvectors of the 
original depolarization tensor $\mathbf{N}(\mathbf{r})$.

>>>>

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any uniformly magnetized body in a given direction.
By presuming that this uniform magnetization is due to
induction and that it is proportional to the resulting
magnetic field (intensity) inside the body, he postulated 
that the resulting field must also be uniform and 
parallel to the magnetization. This uniformity is due to
the fact that the resulting field is defined as the
negative gradient of the magnetic scalar potential.
As a consequence of this uniformity, 
the gravitational potential $U$ at points within the 
body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform inducing magnetic field.
This property can be extended to other bodies
defined as limiting cases of an ellipsoid
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field.

@@

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre
(Fig. \ref{fig:orientation-angles}b).
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
(Eq. \ref{eq:A}) is defined according to the ellipsoid type.
Subsequently, quantities referred to the local coordinate system
(Fig. \ref{fig:orientation-angles}b) are represented with
the simbol "$\sim$".

@@

Consider a magnetized ellipsoid immersed in
a uniform inducing magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
given by
\begin{equation}
\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
\begin{array}{c}
\cos I \: \cos D \\
\cos I \: \sin D \\
\sin I
\end{array}
\right] \: ,
\label{eq:H0}
\end{equation}
where $\| \cdot \|$ denotes the Euclidean norm and
$D$ and $I$ are respectively, the declination and inclination of the 
local-geomagnetic field in the main coordinate system
(Fig. \ref{fig:orientation-angles}a).
This field represents the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:V-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Eq. \ref{eq:V-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896, reitz1992, sttraton2007}.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system (Fig. \ref{fig:orientation-angles}a)
into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system (Fig. \ref{fig:orientation-angles}b).
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
peake1953, macmillan1958, chang1961, lowes1974,  clark1986, 
tejedor1995, sttraton2007}.

@@

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in 
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$ 
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq.\ref{eq:M-remanence} by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

@@

The magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
produced by an ellipsoid at external points is calculated from 
Eqs. \ref{eq:H-tilde} and \ref{eq:M-remanence} as the difference
between the resultant field $\mathbf{H}(\mathbf{r})$ 
and the inducing field $\mathbf{H}_{0}$:
\begin{equation}
\Delta \mathbf{H}(\mathbf{r}) = 
- \mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
\mathbf{M} \: .
\label{eq:delta-H}
\end{equation}
The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
Eq. \ref{eq:delta-H} will be presented in
the following section.

The $\Delta \mathbf{H}(\mathbf{r})$ 
represents the magnetic field produced by a uniformly magnetized 
body located in the crust.
Equation \ref{eq:delta-H} gives the magnetic field
(in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
in geophysics, the most widely used field is the magnetic 
induction (in \unit{nT}). Fortunately, this conversion can
be easily done by multiplying Eq. \ref{eq:delta-H}
by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
magnetic constant (in \unit{H \, m^{-1}}).
For geophysical applications, it is preferable to
calculate the total-field anomaly produced by the
magnetic sources. This scalar quantity is given by
\citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) = \| 
\mathbf{B}_{0} + \Delta \mathbf{B}(\mathbf{r}) \|
- \| \mathbf{B}_{0} \| \: ,
\label{eq:delta-T}
\end{equation}
where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
and $\Delta \mathbf{B}(\mathbf{r}) = 
k_{m} \, \Delta \mathbf{H}(\mathbf{r})$,
with $\mathbf{H}_{0}$ and $\Delta \mathbf{H}(\mathbf{r})$ defined,
respectively, by Eqs. \ref{eq:H0} and \ref{eq:delta-H}.
In practical situations, however, 
$\| \mathbf{B}_{0} \| >> \| \Delta \mathbf{B}(\mathbf{r}) \|$
and, consequently, the following approximation is valid \citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) \approx  
\frac{\mathbf{B}_{0}^{\top} \Delta \mathbf{B}(\mathbf{r})}{\| \mathbf{B}_{0} \|} \: .
\label{eq:delta-T-approx}
\end{equation}

@@

The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\dagger}$ used in the previous sections
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by 
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the  
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the 
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the SI
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
Notice that, according to Eqs. \ref{eq:H-tilde} 
and \ref{eq:N-tilde-VT-N-V},
\begin{equation}
\mathbf{N}(\mathbf{r}) = 
\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
\mathbf{V}^{\top} \: ,
\label{eq:N-V-N-dagger-VT}
\end{equation}
where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
This equation shows that, for the particular case 
in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
represent a point inside the
volume $\vartheta$ of the ellipsoid, the elements 
$\tilde{n}^{\dagger}_{ii}$ (Eq. \ref{eq:n-tilde-dagger-ii})
of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
columns of $\mathbf{V}$ represent the eigenvectors of the 
original depolarization tensor $\mathbf{N}(\mathbf{r})$.
